---
title: "Boolean Practice"
author: "Paloma Cartwright"
date: "06/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Taking a look at `starwars`

- `include = `: show or hide everything 
- `echo = `: show or hide code 

```{r}
#summary of starwars 
#summary(starwars)

#look at the first few lines 
head(starwars)

#check out dimensions
dim(starwars)
```

```{r, warning = FALSE}
ggplot(data = starwars, aes(x = height, y = mass)) + 
  geom_point(aes(color = gender))
```

## Exploring the Starwars dataset with boolean logic 

#### Find the mean, variance and standard deviation of character height 

```{r}
print(sw_height_mean <- mean(starwars$height, na.rm = TRUE))
## Height is found in cm 
```

```{r}
print(sw_height_var <- var(starwars$height, na.rm = TRUE))
# Variance is found in cm squared 
```

```{r}

print(sw_height_sd <- sd(starwars$height, na.rm = TRUE))
## standard deviation is found in cm
```

Mean character height is `r round(sw_height_mean, 1)`cm with a standard deviation of `r round(sw_height_sd, 1)`cm.


# Logical Expressions
### Trying words 
```{r}

"cat" > "armadillo"

"cat" > "elephant"

"teddy" == "teddy"
```

### Trying numbers 

```{r}
10 <= 11

5 >= 4

3 <= 1
```

### Playing with vectors 
```{r}

tarantulas <- c(1, 3, 7, 10, 15)

tarantulas > 5
```
### Logical Operators 

- `!`
- `&`
- `|`


```{r}
3 < 1 | 8 > 2

6 < 10 & 5 < 1

10 != 5

4 != 4 | 2 < 5 | 6 > 10

0 == FALSE

1 == TRUE 

```

